Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-15 paper/main.tex
methods: honing & typos (v2)

@@

% AD annotation
For the analysis of the AD stimulus, we extended a publicly available annotation
of speech \citep{hausler2021studyforrest} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of (concrete and countable) nouns that
the narrator uses to describe the movie's missing visual content based on a set
of rules.
% preliminary annotation
A preliminary annotation was performed by one person according to the rules.
% corrections
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, the rule for a word to belong to
a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories (see Table
\ref{tab:ao-events}). These event categories were then used to model hemodynamic
responses.

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[h!]
    \caption{Categories and rules to categorize the descriptive nouns spoken by
        the audio-description's narrator.
        Examples are given in English.
        Some of these initial 18 noun categories were pooled resulting in 11
        event categories that served as a basis to build the regressors of the
        GLM
        (cf. Table \ref{tab:ao-events}).
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe
\tabularnewline
face & face or parts of it & face, ear, nose, mouth
\tabularnewline
female & female person & nurse, mother, woman
\tabularnewline
females & female persons & women
\tabularnewline
fname & female name & Jenny
\tabularnewline
furniture & movable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
\tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet
\tabularnewline
male & male person & man, father, soldier
\tabularnewline
males & male persons & boys, opponents
\tabularnewline
mname & male name & Bubba, Kennedy
\tabularnewline
object & countable entity with firm boundaries & telephone, car
\tabularnewline
objects & countable entities & wheels, plants
\tabularnewline
persons & concrete persons of unknown sex & hippies, patients
\tabularnewline
setting\_new & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
setting\_rec & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

    into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead};
    \texttt{object}), \texttt{fg\_ad\_lrdiff} (left-right volume difference)
    and \texttt{fg\_ad\_rms} (root mean square volume) represent one event for
    every movie frame (\unit[40]{ms}).

@@

body & trunk of the body or overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII

@@

furn & moveable furniture insides \& outsides & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII

@@

object & inanimate entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII

@@

se\_new & noun describing an unfamiliar setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII

@@

se\_old & noun describing a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII

@@

% low-leve confounds: intro
Lastly, we algorithmically annotated the temporal structure of low-level
perceptual features to create nuisance regressors.
% visual shit
For the AV stimulus, we computed the mean luminance of a movie frame
(\unit[40]{ms}), the difference in mean luminance of each frame's left and right
half, the difference in mean luminance of the lower and upper half, and finally
the perceptual difference of consecutive frames.
% auditory shit
Finally, we computed the left-right difference in volume and root mean square
energy averaged across the length of every movie frame (\unit[40]{ms}) of both
audio-tracks.

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as box car events of 200 ms duration.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame AO:
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).
% we checked correlations
Since we annotated events in naturalistic stimuli and thus fixed time courses
that could not experimentally manipulated, the modeled time-series [of
hemodynamic activity] based on these events could be correlated leading to
shared variance and thus low detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% (highest) correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
% no surprise
This was expected and served as a ``sanity check'' since the audio-track of the
audio-description is the audio-track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

>>>>

    the segments that were used for the eight sessions of fMRI scanning).

@@

% AD annotation
For the analysis of the AD stimulus, we extended a publicly available annotation
of speech \citep{hausler2021studyforrest} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of (concrete and countable) nouns that
the narrator uses to describe the movie's missing visual content based on a set
of rules.
% preliminary annotation
A preliminary annotation was performed by one person according to the rules.
% corrections
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, the rule for a word to belong to
a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another category in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories (see Table
\ref{tab:ao-events}). These event categories were then used to model hemodynamic
responses.

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[h!]
    \caption{Categories and rules to categorize the nouns spoken by
        the audio-description's narrator.
        Examples are given in English.
        Some of these initial 18 noun categories were pooled resulting in 11
        event categories that served as basis to build the regressors of the
        GLM
        (cf. Table \ref{tab:ao-events}).
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
bodypart & limbs & arm, finger, leg, toe
\tabularnewline
face & face or parts of it & face, ear, nose, mouth
\tabularnewline
female & female person & nurse, mother, woman
\tabularnewline
females & female persons & women
\tabularnewline
fname & female name & Jenny
\tabularnewline
    furniture & movable furniture (insides \& outsides) & bench, bed, table,
    chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
\tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck;
helmet
\tabularnewline
male & male person & man, father, soldier
\tabularnewline
males & male persons & boys, opponents
\tabularnewline
mname & male name & Bubba, Kennedy
\tabularnewline
object & countable entity with firm boundaries & telephone, car
\tabularnewline
objects & countable entities & wheels, plants
\tabularnewline
persons & concrete persons of unknown sex & hippies, patients
\tabularnewline
setting\_new & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
setting\_rec & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

    into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead},
    \texttt{object}).

@@

body & trunk of the body; overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII

@@

furn & moveable furniture (insides \& outsides) & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII

@@

object & countable entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII

@@

se\_new & a setting occurring for the first time & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII

@@

se\_old & a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII

@@

% low-leve confounds: intro
Lastly, we algorithmically annotated the temporal structure of low-level
perceptual features to create nuisance regressors.
% visual shit
For the AV stimulus, we computed the mean luminance of a movie frame
(\unit[40]{ms}), the difference in mean luminance of each frame's left and right
half, the difference in mean luminance of the lower and upper half, and finally
the perceptual difference of consecutive frames.
% auditory shit
Finally for both audio tracks, we computed the left-right difference in volume
and root mean square energy averaged across the length of every movie frame
(\unit[40]{ms}).

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as box car events of 200 ms duration.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame AO:
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).
% we checked correlations
Since we annotated events in naturalistic stimuli and thus fixed time courses
that could not experimentally manipulated, the modeled time-series [of
hemodynamic activity] based on these events could be correlated leading to
shared variance and thus low detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% (highest) correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
% no surprise
This was expected and served as a ``sanity check'' since the audio track of the
audio-description is the audio track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.
